Incentivizing Exploration with Unbiased History

### 2018-10-16 model.tex
ok.

We study the mult-armed bandit problem in a social learning context,
in which a principal faces a sequence of $T$ myopic agents. There is a
set $\A$ of $K$ arms, and the reward from pulling an arm $a\in \A$ is
distributed according to the Bernoulli distribution with an unknown
mean $\mu_a$.\swcomment{do we plan to generalize to real-valued?}  At
each round $t\in [T]$, a new agent $t$ arrives, receives a message
$m_t$ from the principal, chooses an arm $a_t\in \A$, and collects a
reward $r_t\in \{0,1\}$ that is immediately observed by the
principal.

@@

\xhdr{Unbiased sub-history policy.} The principal computes the
sequence of messages $m_t$ according to a disclosure policy. We will
focus on \emph{unbiased sub-history policies} that at each round $t$
reveal the \emph{sub-history} in a subset of previous rounds
$S_t\subseteq [t-1]$: $\{(s, a_s, r_s)\mid s \in S_t\}$, where the
subset $S_t$ is fixed ahead of time. A simple example is the policy
that reveals the \emph{full history}, that is $S_t = [t-1]$.  All of
the policies we develop are \emph{transitive}: for any two agents $t$
and $t'$ such that $t'\in S_t$, then the sub-history of $S_t$ contains
that of $S_{t'}$.

@@

The first assumption ensures that the reward distributions have
sufficient entropy to induce natural exploration. We choose the
bounded range $[1/3, 2/3]$ for the simplicity of our analysis, and it
can further relaxed to $[1/C, (C-1)/C]$ for any constant $C$.

We allow different agents to have different behavior models as long as
they satisfy Assumption \ref{ass:embehave}. More specifically, we
assume each agent's behavior model is sampled from an unknown
distribution independently.\swcomment{why independently? can be be
  adversarial?}
\begin{remark}
how this relates to Bayesian exploration with conjugate priors
\end{remark}

\swcomment{todo: define regret. define gap $\Delta$}

Given any sequence of arms $\{a_1, \ldots, a_T\}$ chosen by the agents, the \emph{regret} is defined as
\[
  \reg(a_1, \ldots , a_T) = T \max_{a\in \A} \mu_a - \sum_{t=1}^T
  \mu_{a_t}.
\]

The principal's goal is then to design a policy to minimize the regret
from the induced sequence arms chosen by agents.

>>>>

We study the mult-armed bandit problem in a social learning context,
in which a principal faces a sequence of $T$ myopic agents. There is a
set $\A$ of $K$ arms, and the reward from pulling an arm $a\in \A$ is
distributed according to the Bernoulli distribution with an unknown
mean $\mu_a$.\swcomment{do we plan to generalize to real-valued?}  At
each round $t\in [T]$, a new agent $t$ arrives, receives a message
$m_t$ from the principal, chooses an arm $a_t\in \A$, and collects a
reward $r_t\in \{0,1\}$ that is immediately observed by the
principal. Given any sequence of arms $\{a_1, \ldots, a_T\}$ chosen by
the agents, the \emph{regret} is defined as
\[
  \reg(T)= \reg(a_1, \ldots , a_T) = T \max_{a\in \A} \mu_a -
  \sum_{t=1}^T \mu_{a_t}.
\]

@@

\xhdr{Unbiased sub-history policy.} The principal's goal is to reveals
a sequence of messages accroding to a disclosure policy so that the
regret of the induced sequence of actions is minimized. We will focus
on \emph{unbiased sub-history policies} that at each round $t$ reveal
the \emph{sub-history} in a subset of previous rounds
$S_t\subseteq [t-1]$: $\{(s, a_s, r_s)\mid s \in S_t\}$, where the
subset $S_t$ is fixed ahead of time. A simple example is the policy
that reveals the \emph{full history}, that is $S_t = [t-1]$.  All of
the policies we develop are \emph{transitive}: for any two agents $t$
and $t'$ such that $t'\in S_t$, then the sub-history of $S_t$ contains
that of $S_{t'}$.

@@

The first assumption ensures that the reward distributions have
sufficient entropy to induce natural exploration. We choose the
bounded range $[1/3, 2/3]$ for the simplicity of our analysis, and it
can further relaxed to $[1/C, (C-1)/C]$ for any constant $C$. The
second assumption says that the estimates computed by the agents are
well-behaved, and are close to the empirical estimates given by the
sub-history, provided that the number of observations is sufficiently
large.

We allow different agents to have different behavior models as long as
they satisfy Assumption \ref{ass:embehave}. More specifically, we
assume each agent's behavior model is sampled from an unknown
distribution independently.\swcomment{why independently? can be be
  adversarial?}
\begin{remark}
  how this relates to Bayesian exploration with conjugate
  priors\swcomment{seems to be something nasty}
\end{remark}

Given any bandit instance, we can also define the \emph{gap parameter}
$\Delta$ as the difference between the largest and second largest mean
rewards. In general, the gap parameter is unknown to the principal (or
the algorithm), but we also show how we can obtain different forms of
regret bounds if $\Delta$ is known.
